Manuscript 1 code

### 2024-11-27 manuscript_1_code.Rmd
Still more axis corrections

(alpha_gamma_stability_plot <- 
  ggplot() +
  geom_point(data = dss_spatial_2,
             aes(x = stability_mean, y = cover_stability, colour = habitat), size = 1, alpha = 0.5) + 
  geom_line(data = filtered_ag_effects, aes(x = stability_mean, y = exp(yvar), colour = habitat), size = 1.5) +
  geom_ribbon(data = filtered_ag_effects, aes(x = stability_mean, ymin = exp(LCL), ymax = exp(UCL), fill = habitat),
              alpha = 0.3) +
  scale_colour_manual(values = habitat_colours) +
  scale_fill_manual(values = habitat_colours) +
  labs(y = "", x = "Plot stability", title = "") +
  trends_theme
         )
```

>>>>

(alpha_gamma_stability_plot <- 
  ggplot() +
  geom_point(data = dss_spatial_2,
             aes(x = stability_mean, y = cover_stability, colour = habitat), size = 1, alpha = 0.5) + 
  geom_line(data = filtered_ag_effects, aes(x = stability_mean, y = exp(yvar), colour = habitat), size = 1.5) +
  geom_ribbon(data = filtered_ag_effects, aes(x = stability_mean, ymin = exp(LCL), ymax = exp(UCL), fill = habitat),
              alpha = 0.3) +
  scale_colour_manual(values = habitat_colours) +
  scale_fill_manual(values = habitat_colours) +
  labs(y = "", x = "Plot-level stability", title = "") +
  trends_theme
         )
```
